Age-related changes in plant growth and traits

### 2016-12-20 Analysis-accessory.Rmd
Edits to Accessory Figs manuscript, including reworking Figure 1 and accompanying text and work on discussion.
Some work on Tables for Supp Material

#Figure 01. predictions
```{r}
png("ms/Accessory/output/Figure01b&c_predictions.png", height=3, width=6, units="in", res=300)
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="count, scaled to plant size",side=2,line=1.1,outer=FALSE,cex=0.8)
mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("seed count by reproductive costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("b",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="choosiness (ovule:seed)",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs,",side=1,line=1.1,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=1,line=1.9,outer=FALSE,cex=0.8)
extra.top.left("c",2,1)
dev.off()

png("ms/Accessory/output/Figure01def_predictions.png", height=6, width=6, units="in", res=300)

par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05))
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
extra.top.left("d",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
extra.top.left("e",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
segments(x0=.15,x1=.9,y0=.15,y1=.9,lty=2)
axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
mtext(text="proportion total success costs",side=2,line=1.8,outer=FALSE,cex=0.8)
mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("f",2,1)

@@

>>>>

#Figure 01. predictions
```{r}
png("ms/Accessory/output/Figure01b&c&d_predictions.png", height=3.6, width=9, units="in", res=300)
par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.6,.05))
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="b.  Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Seed count-reproductive costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="seed count,",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="reproductive costs",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
#extra.top.left("b",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="c.  Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Ovule count-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="mature ovules count,",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
#extra.top.left("c",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="d.  Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Choosiness-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="choosiness",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="(ovule:seed)",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs,",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=1,line=1.2,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=2.1,outer=FALSE,cex=0.8)
#extra.top.left("d",2,1)
dev.off()

# png("ms/Accessory/output/Figure01def_predictions.png", height=6, width=6, units="in", res=300)
# 
# par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05))
# plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
# segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
# segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
# axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
# axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
# mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
# mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
# legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
# extra.top.left("d",2,1)
# 
# plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
# segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
# segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
# axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
# axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
# mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
# mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
# legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
# extra.top.left("e",2,1)
# 
# plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
# segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
# segments(x0=.15,x1=.9,y0=.15,y1=.9,lty=2)
# axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
# axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
# mtext(text="proportion total success costs",side=2,line=1.8,outer=FALSE,cex=0.8)
# mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
# legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
# extra.top.left("f",2,1)
# 
# dev.off()
```

@@

plot(choosiness2~prop_pollen_attract_vs_all_repro,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(.002,.3),ylim=c(3,800),yaxt="n",cex=1,ylab="",xlab="",xaxt="n")
axis(2, at=c(10,100,1000), labels=c(10,100,1000),cex.axis=0.8,las=2)
axis(1, at=c(0.01,0.1), labels=c(0.01,0.1),cex.axis=0.8)
mtext("pollen-attractions costs, scaled to leaf area",1,line=1.7,cex=0.7)
mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
#mod_choosy <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
mod_choosy2 <- sma(choosiness2~prop_pollen_attract_vs_all_repro,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")

### 2016-12-20 scripts/Accessory_figs_20160905.Rmd
Edits to Accessory Figs manuscript, including reworking Figure 1 and accompanying text and work on discussion.
Some work on Tables for Supp Material

#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
```{r}
win.metafile("ms/Accessory/Figure_SXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
plot

par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
options(scipen = 2)

xvar <- "repro_inv"
yvar <- "accessory_costs"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

write.csv(results, file="ms/Accessory/Table05a_accessory_vs_all_repro.csv",row.names=FALSE)

@@

write.csv(results, file="ms/Accessory/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)

@@

write.csv(results, file="ms/Accessory/Table05c_accessory_vs_age.csv",row.names=FALSE)
dev.off()
```

>>>>

#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
```{r}
xvar <- "repro_inv"
yvar <- "accessory_costs"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

write.csv(results, file="ms/Accessory/output/TableS3a_accessory_vs_all_repro.csv",row.names=FALSE)

@@

write.csv(results, file="ms/Accessory/output/TableS3b_accessory_vs_total_weight.csv",row.names=FALSE)

@@

write.csv(results, file="ms/Accessory/output/TableS3c_accessory_vs_age.csv",row.names=FALSE)
```
